Type cones of $\b{g}$-vector fans

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
linearity space

Unfortunately, \cref{lem:linearDependencegvectorsCA} is less precise than \cref{prop:exchangeablePairsAsso}. Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
We will prove however that it is independent of the seeds containing~$x$ and~$x'$.

@@

\[
\begin{array}{r|ccccccccc}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
\text{lines}		& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
					& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
\text{lines}		& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
					& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
\end{array}
\]

@@

\begin{definition}
Consider a seed~$(\B, \cluster)$ and a cluster variable~$x \in \cluster$. The mutation of~$\seed$ in direction~$x$ is a \defn{mesh mutation} if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative, or all non-positive.
\end{definition}

For instance, in the initial seed~$(\B_\circ, \cluster_\circ)$, the mutation in the direction of any variable~${x_\circ \in \cluster_\circ}$ is a mesh.
We call these meshes \defn{initial}.
We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two non-initial cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a mesh mutation.
The following statement describes the other meshes.

@@

\begin{lemma}
\label{lem:dependenceMesh}
Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ such that the entries~$b_{xy}$ for~$y \in \cluster$ are all non-positive or all non-negative.
If either~$x$ or~$x'$ is an initial cluster variable, then
\[
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = 0.
\]
Otherwise, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy the linear dependence
\[
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \sum_{y \in \cluster \cap \cluster'} |b_{xy}| \, \gvectorFull{\B_\circ}{y}.
\]
\end{lemma}

@@

\[
\begin{array}{r|cccccccc}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{lines}		& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
					& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{lines}		& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
					& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{lines}		& 
					& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{lines}		& 
					& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

@@

\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}

>>>>

Unfortunately, \cref{lem:linearDependencegvectorsCA} is less precise than \cref{prop:exchangeablePairsAsso}. Indeed, which of the two possible linear dependences is satisfied by the $\b{g}$-vectors of~$\cluster \cup \cluster'$ depends on the initial exchange matrix~$\B_\circ$.
We will prove however that it is independent of the seeds containing~$x$ and~$x'$.
\vincent{Link to \cref{sec:clusterCategories}.}

@@

\[
\begin{array}{r|ccccccccc}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
\end{array}
\]

@@

\begin{definition}
%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
\end{definition}

We denote by~$\meshes$ the set of all pairs~$(x,x')$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.

@@

\begin{lemma}
\label{lem:dependenceMesh}
Consider two adjacent seeds~${(\B, \cluster)}$ and~${(\B', \cluster')}$ with~$\cluster \ssm \{x\} = \cluster' \ssm \{x'\}$ connected by a mesh mutation.
If the mesh mutation is initial, then
\[
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = 0.
\]
Otherwise, the $\b{g}$-vectors of~$\cluster \cup \cluster'$ with respect to~$\B_\circ$ satisfy the linear dependence
\[
\gvectorFull{\B_\circ}{x} + \gvectorFull{\B_\circ}{x'} = \sum_{y \in \cluster \cap \cluster'} |b_{xy}| \, \gvectorFull{\B_\circ}{y}.
\]
\end{lemma}

@@

\[
\begin{array}{r|cccccccc}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA11}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA12}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA13}}  \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 
\text{space}		& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{tubeB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \\ %\compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 
\text{space}		& \\[.2cm]
\text{inequalities} & \\[.2cm]
\end{array}
\]

@@

\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
\label{sec:clusterCategories}
